---
title: 'September 2018 review: Microbial communities performing dissimilatory nitrate
  reduction to ammonium in Australian forest and agricultural soils'
author: "Eric Ireland"
date: "4 September 2018"
output:
  html_document: default
  pdf_document: 
    latex_engine: xelatex
  word_document: default

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lattice)
library(readr)
library(ggplot2)
library(scales)
library(car)
library(tidyverse)
library(readxl)
library(knitr)
library(kableExtra)

narG <- read_csv("narG.csv")
# nirS <- read_csv("nirS.csv")
# AOA_amoA <- read_csv("AOA_amoA.csv")
nosZ <- read_csv("nosZ.csv")
rRNA16S <- read_csv("bact16S.csv")
nirK <- read_csv("nirK.csv")
nrfA <- read_csv("nrfA.csv")
```

### Baw Baw HWC/nitrate ratios

``` {r echo=FALSE}
bawbaw_TOC_50to59 <- read_table2(col_names = FALSE, "TOC_results/2018-07-02_Baw_Baw_50to59_diluted_1to20.txt", skip = 13)


newnames <- scan("50to59_sample_names", character(), quote = "") #replace "untitled" with sample names in 50to59
bawbaw_TOC_50to59$X3 <- newnames
bawbaw_TOC_50to59 %>%
  rename(`Sample name` = X3, `sample ID`=X4, `TOC mg/L` = X5, `TC mg/L` = X6, `IC mg/L` = X7) %>%
  select(`Sample name`:`IC mg/L`) %>%
  write_csv("TOC_results/2018-07-02_Baw_Baw_50to59_diluted_1to20_filtered_results.csv") # write raw results to csv file for printing in lab notebook

bawbaw_TOC_50to59$X3 <- gsub("m_SP.*", "", bawbaw_TOC_50to59$X3) # remove "_SP.*" from "summit" sample names to just give elevation.
bawbaw_TOC_50to59$X3 <- gsub("_SP.*", "", bawbaw_TOC_50to59$X3) # remove "_SP.*" from "summit" sample names to just give elevation.

bawbaw_TOC_60to97 <- read_table2(col_names = FALSE, "TOC_results/2018-07-04_Baw_Baw_60to97_diluted_1to20.txt", skip = 13)
bawbaw_TOC_60to97 %>%
  rename(`Sample name` = X3, `sample ID`=X4, `TOC mg/L` = X5, `TC mg/L` = X6, `IC mg/L` = X7) %>%
  select(`Sample name`:`IC mg/L`) %>%
  write_csv("TOC_results/2018-07-02_Baw_Baw_60to97_diluted_1to20_filtered_results.csv") # write raw results to csv file for printing in lab notebook


bawbaw_TOC_60to97 <- bawbaw_TOC_60to97[-c(4, 20), ] # delete 200SP2_... because they are duplicates (mislabelled?)
bawbaw_TOC_60to97$X3 <- gsub("m_SP.*", "", bawbaw_TOC_60to97$X3) # remove "_SP.*" from sample names to just give elevation.
bawbaw_TOC_60to97$X3 <- gsub("_SP.*", "", bawbaw_TOC_60to97$X3) # remove "_SP.*" from "summit" sample names to just give elevation.


bawbaw_TOC_means <- bind_rows(bawbaw_TOC_50to59, bawbaw_TOC_60to97) %>%
  rename(elevation = X3, TOC_mg_per_l = X5) %>%
  select(elevation, TOC_mg_per_l) %>%
  mutate(elevation=replace(elevation, elevation=="summit", "1500")) %>%
  mutate(TOC_mg_per_l_before_dilution = TOC_mg_per_l*20) %>% 
  mutate(mg_TOC_per_30ml = TOC_mg_per_l_before_dilution * 0.030) %>%
  mutate(ug_TOC_per_30ml = mg_TOC_per_30ml * 1000 ) %>% 
  mutate(ug_TOC_per_g_soil = ug_TOC_per_30ml / 3) %>% # calculate original concentration
  group_by(elevation) %>% 
  summarise(mean_ug_TOC_per_g_soil = mean(ug_TOC_per_g_soil))

# read mineral N data

bawbaw_mineral_N <- read_excel("18. 3422 Eric 180704 - SFA Report 18.07.10.xls", 
                                                       skip = 14) #read KCl data

bawbaw_mineral_N[bawbaw_mineral_N=="<0.2"] <- 0.2 # N.B.!! first need to convert <0.2 to 0.2
bawbaw_mineral_N$sample <- gsub("SP.", "", bawbaw_mineral_N$sample) # remove "SP." from sample names to just give elevation.

bawbaw_mineral_N_means <- bawbaw_mineral_N %>%
  rename(elevation = sample, nitrate = `N-Nitrate (mg/L)`, ammonium = `N-Ammonium (mg/L)`) %>% #rename column to make it easier to type!
  select(elevation, nitrate, ammonium) %>% #just keep the necessary data columns
  filter(elevation != "blank") %>% # remove blank samples
  mutate(nitrate = as.numeric(nitrate)) %>% # convert from character to numeric data
  mutate(ammonium = as.numeric(ammonium)) %>% # convert from character to numeric data
  mutate(elevation =replace(elevation, elevation=="summit", "1500")) %>% # replace "summit" with "1500"
  mutate(total_NO3_in_extract_mg = nitrate * 0.1,
             total_NO3_in_extract_ug = total_NO3_in_extract_mg * 1000,
             total_NO3_per_g_soil_ug = total_NO3_in_extract_ug / 10) %>% # calculate mean for nitrate
  mutate(total_NH4_in_extract_mg = ammonium * 0.1,
         total_NH4_in_extract_ug = total_NH4_in_extract_mg * 1000,
         total_NH4_per_g_soil_ug = total_NH4_in_extract_ug / 10) %>% # calculate mean for ammonium
  group_by(elevation) %>% 
  summarise_at(c("total_NO3_per_g_soil_ug", "total_NH4_per_g_soil_ug"), mean)


# calculate C/NO3- ratio and C/mineral-N ratio
combined_NC_means <- bind_cols(bawbaw_mineral_N_means, bawbaw_TOC_means)
combined_NC_means <- combined_NC_means %>% select(-elevation1) %>% #remove extra elevation column
  mutate(C_nitrate_ratio = mean_ug_TOC_per_g_soil / total_NO3_per_g_soil_ug,
                                                  C_mineral_N_ratio = mean_ug_TOC_per_g_soil / (total_NO3_per_g_soil_ug + total_NH4_per_g_soil_ug))

# write .rds and .csv and .tsv file with data
write_rds(combined_NC_means,"combined_NC_means.rds")
write_csv(combined_NC_means,"combined_NC_means.csv")
write_tsv(combined_NC_means,"combined_NC_means.tsv")



#print see https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
combined_NC_means2 <- combined_NC_means
combined_NC_means2$C_nitrate_ratio <- round(combined_NC_means2$C_nitrate_ratio, 1)
combined_NC_means2$C_mineral_N_ratio <- round(combined_NC_means2$C_mineral_N_ratio, 1)
combined_NC_means2 <- combined_NC_means2 %>%
  mutate(elevation = factor(elevation, levels = c("200", "300", "500", "600", "800", "900", "1000", "1100","1200", "1300", "1400","1500"))) %>% 
  arrange(elevation) %>% 
  select(elevation, C_nitrate_ratio, C_mineral_N_ratio) 
names(combined_NC_means2) <- c("Elevation", "HWC/nitrate-N", "HWC/mineral-N")
kable(combined_NC_means2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```


#### Bacterial 16S rRNA abundance


```{r rRNA16S, echo=FALSE, fig.cap="Results of qPCR for *rRNA16S* gene. Error bars show SEM. Efficiency = 100.2%, $R^{2} = 0.99$. \\label{rRNA16Sgraph}"}
rRNA16S$copiespergram <- (rRNA16S$SQ*1000)/0.25 #100µL of solution is recovered from 0.25g soil. This template DNA is diluted 1:10 and then 1µL of that diluted DNA is used as template. So we're counting copies of DNA in 0.1µL of template. So, we are using 0.001 (1/100th) of the original DNA. So, times by 100 to get the amount in 100µL DNA, then times by 4 (i.e. divide by 0.25) to get the copies in 1g of soil.
rRNA16S$log10copiespergram <- log10((rRNA16S$SQ*1000)/0.25) #log base 10 transform data
rRNA16S$logecopiespergram <- log((rRNA16S$SQ*1000)/0.25) #log base e transform data

# colnames(rRNA16S)[3] <- "time" # renamed day column to time



### works!!

#summarySE function for errorbars from http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/#Helper%20functions
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}

rRNA16S_summary <- summarySE(rRNA16S, measurevar="logecopiespergram", groupvars="sample_elevation") #not sure if this is correct!

rRNA16S2 <- rRNA16S_summary
rRNA16S2$sample_elevation <- factor(rRNA16S2$sample_elevation, levels=c("200","300","500","600","800","900","1000","1100","1200","1300","1400","1500"))
# rRNA16S2$time <- factor(rRNA16S2$time)


# Error bars represent standard error of the mean
ggplot(rRNA16S2, aes(x=sample_elevation, y=logecopiespergram)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=logecopiespergram-se, ymax=logecopiespergram+se),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+
  labs(
    x = "sample elevation (m)",
    y = "log(copies per gram soil)"
  )
```

```{r echo=FALSE}
linear.model.rRNA <- lm(formula = logecopiespergram ~ sample_elevation, data = rRNA16S)
anovatablerRNA <- Anova(linear.model.rRNA, type="II")
rRNAp <- unname(anovatablerRNA$`Pr(>F)`[1])
```

<!-- could use `r round(rRNAp,3)` to report p value. -->
16S rRNA gene abundance did differ significantly between elevations (*F*-test, $p=`r ifelse(round(rRNAp, 3) == 0, "<.001", round(rRNAp, 3))`$).


```{r nosZ, echo=FALSE, fig.cap="Results of qPCR for *nosZ* gene. Error bars show SEM. Efficiency = 78.4%, $R^{2} = 0.99$. \\label{nosZgraph}"}
nosZ$copiespergram <- (nosZ$SQ*1000)/0.25 #100µL of solution is recovered from 0.25g soil. This template DNA is diluted 1:10 and then 1µL of that diluted DNA is used as template. So we're counting copies of DNA in 0.1µL of template. So, we are using 0.001 (1/100th) of the original DNA. So, times by 100 to get the amount in 100µL DNA, then times by 4 (i.e. divide by 0.25) to get the copies in 1g of soil.
nosZ$log10copiespergram <- log10((nosZ$SQ*1000)/0.25) #log base 10 transform data
nosZ$logecopiespergram <- log((nosZ$SQ*1000)/0.25) #log base e transform data

# colnames(nosZ)[3] <- "time" # renamed day column to time



### works!!

#summarySE function for errorbars from http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/#Helper%20functions
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}

nosZ_summary <- summarySE(nosZ, measurevar="logecopiespergram", groupvars="sample_elevation") #not sure if this is correct!

nosZ2 <- nosZ_summary
nosZ2$sample_elevation <- factor(nosZ2$sample_elevation, levels=c("200","300","500","600","800","900","1000","1100","1200","1300","1400","1500"))
# nosZ2$time <- factor(nosZ2$time)


# Error bars represent standard error of the mean
ggplot(nosZ2, aes(x=sample_elevation, y=logecopiespergram)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=logecopiespergram-se, ymax=logecopiespergram+se),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+
  labs(
    x = "sample elevation (m)",
    y = "log(copies per gram soil)"
  )
```


```{r echo=FALSE}
linear.model.nosZ <- lm(formula = logecopiespergram ~ sample_elevation, data = nosZ)
anovatablenosZ <- Anova(linear.model.nosZ, type="II")
nosZ_p <- unname(anovatablenosZ$`Pr(>F)`[1])
```


<!-- could use `r round(rRNAp,3)` to report p value. -->
*nosZ* gene abundance varied between elevations (*F*-test, $p=`r ifelse(nosZ_p < 0.01, "<0.01", ifelse(nosZ_p < 0.05, "<0.05",round(nosZ_p, 3)))`$).


```{r narG, echo=FALSE, fig.cap="Results of qPCR for *narG* gene. Error bars show SEM. Efficiency = 85.3%, $R^{2} = 0.99$. \\label{narGgraph}"}
narG$copiespergram <- (narG$SQ*1000)/0.25 #100µL of solution is recovered from 0.25g soil. This template DNA is diluted 1:10 and then 1µL of that diluted DNA is used as template. So we're counting copies of DNA in 0.1µL of template. So, we are using 0.001 (1/100th) of the original DNA. So, times by 100 to get the amount in 100µL DNA, then times by 4 (i.e. divide by 0.25) to get the copies in 1g of soil.
narG$log10copiespergram <- log10((narG$SQ*1000)/0.25) #log base 10 transform data
narG$logecopiespergram <- log((narG$SQ*1000)/0.25) #log base e transform data

# colnames(narG)[3] <- "time" # renamed day column to time



### works!!

#summarySE function for errorbars from http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/#Helper%20functions
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}

narG_summary <- summarySE(narG, measurevar="logecopiespergram", groupvars="sample_elevation") #not sure if this is correct!

narG2 <- narG_summary
narG2$sample_elevation <- factor(narG2$sample_elevation, levels=c("200","300","500","600","800","900","1000","1100","1200","1300","1400","1500"))
# narG2$time <- factor(narG2$time)


# Error bars represent standard error of the mean
ggplot(narG2, aes(x=sample_elevation, y=logecopiespergram)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=logecopiespergram-se, ymax=logecopiespergram+se),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+
  labs(
    x = "sample elevation (m)",
    y = "log(copies per gram soil)"
  )
```


```{r echo=FALSE}
linear.model.narG <- lm(formula = logecopiespergram ~ sample_elevation, data = narG)
anovatablenarG <- Anova(linear.model.narG, type="II")
narG_p <- unname(anovatablenarG$`Pr(>F)`[1])
```


<!-- could use `r round(rRNAp,3)` to report p value. -->
*narG* gene abundance did not vary significantly between elevations (*F*-test, $p=`r ifelse(narG_p < 0.01, "<0.01", ifelse(narG_p < 0.05, "<0.05",round(narG_p, 3)))`$).


```{r nirK, echo=FALSE, fig.cap="Results of qPCR for *nirK* gene. Error bars show SEM. Efficiency = 70.0%, $R^{2} = 0.99$. \\label{nirKgraph}"}
nirK$copiespergram <- (nirK$SQ*1000)/0.25 #100µL of solution is recovered from 0.25g soil. This template DNA is diluted 1:10 and then 1µL of that diluted DNA is used as template. So we're counting copies of DNA in 0.1µL of template. So, we are using 0.001 (1/100th) of the original DNA. So, times by 100 to get the amount in 100µL DNA, then times by 4 (i.e. divide by 0.25) to get the copies in 1g of soil.
nirK$log10copiespergram <- log10((nirK$SQ*1000)/0.25) #log base 10 transform data
nirK$logecopiespergram <- log((nirK$SQ*1000)/0.25) #log base e transform data

# colnames(nirK)[3] <- "time" # renamed day column to time



### works!!

#summarySE function for errorbars from http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/#Helper%20functions
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}

nirK_summary <- summarySE(nirK, measurevar="logecopiespergram", groupvars="sample_elevation") #not sure if this is correct!

nirK2 <- nirK_summary
nirK2$sample_elevation <- factor(nirK2$sample_elevation, levels=c("200","300","500","600","800","900","1000","1100","1200","1300","1400","1500"))
# nirK2$time <- factor(nirK2$time)


# Error bars represent standard error of the mean
ggplot(nirK2, aes(x=sample_elevation, y=logecopiespergram)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=logecopiespergram-se, ymax=logecopiespergram+se),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+
  labs(
    x = "sample elevation (m)",
    y = "log(copies per gram soil)"
  )
```


```{r echo=FALSE}
linear.model.nirK <- lm(formula = logecopiespergram ~ sample_elevation, data = nirK)
anovatablenirK <- Anova(linear.model.nirK, type="II")
nirK_p <- unname(anovatablenirK$`Pr(>F)`[1])
```


<!-- could use `r round(rRNAp,3)` to report p value. -->
*nirK* gene abundance did not vary significantly between elevations (*F*-test, $p=`r ifelse(nirK_p < 0.01, "<0.01", ifelse(nirK_p < 0.05, "<0.05",round(nirK_p, 3)))`$).


```{r nrfA, echo=FALSE, fig.cap="Results of qPCR for *nrfA* gene. Error bars show SEM. Efficiency = 63.4%, $R^{2} = 0.99$. \\label{nrfAgraph}"}
nrfA$copiespergram <- (nrfA$SQ*1000)/0.25 #100µL of solution is recovered from 0.25g soil. This template DNA is diluted 1:10 and then 1µL of that diluted DNA is used as template. So we're counting copies of DNA in 0.1µL of template. So, we are using 0.001 (1/100th) of the original DNA. So, times by 100 to get the amount in 100µL DNA, then times by 4 (i.e. divide by 0.25) to get the copies in 1g of soil.
nrfA$log10copiespergram <- log10((nrfA$SQ*1000)/0.25) #log base 10 transform data
nrfA$logecopiespergram <- log((nrfA$SQ*1000)/0.25) #log base e transform data

# colnames(nrfA)[3] <- "time" # renamed day column to time



### works!!

#summarySE function for errorbars from http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/#Helper%20functions
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}

nrfA_summary <- summarySE(nrfA, measurevar="logecopiespergram", groupvars="sample_elevation") #not sure if this is correct!

nrfA2 <- nrfA_summary
nrfA2$sample_elevation <- factor(nrfA2$sample_elevation, levels=c("200","300","500","600","800","900","1000","1100","1200","1300","1400","1500"))
# nrfA2$time <- factor(nrfA2$time)


# Error bars represent standard error of the mean
ggplot(nrfA2, aes(x=sample_elevation, y=logecopiespergram)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=logecopiespergram-se, ymax=logecopiespergram+se),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+
  labs(
    x = "sample elevation (m)",
    y = "log(copies per gram soil)"
  )
```


```{r echo=FALSE}
linear.model.nrfA <- lm(formula = logecopiespergram ~ sample_elevation, data = nrfA)
anovatablenrfA <- Anova(linear.model.nrfA, type="II")
nrfA_p <- unname(anovatablenrfA$`Pr(>F)`[1])
```


<!-- could use `r round(rRNAp,3)` to report p value. -->
*nrfA* gene abundance varied significantly between elevations (*F*-test, $p=`r ifelse(nrfA_p < 0.01, "<0.01", ifelse(nrfA_p < 0.05, "<0.05",round(nrfA_p, 3)))`$).

